---
title: "HW4"
author: "Evan Mills"
date: "March 5, 2019"
output: html_document
---

```{r}
library(datasets)
library(dplyr)
library(ggplot2)
library(plyr)

chicks <- ChickWeight
```

1.)
```{r}
weight0 <- select(chicks, weight, Chick, Time) %>%
filter(Time == 0)
head(weight0)
```

2.)
```{r}
complete <- chicks %>%
  group_by(Chick) %>%
  filter(n() == 12)

head(complete, 3)
```

3.)
```{r}
complete <- complete %>%
  mutate(complete, weightGain = as.numeric(weight - weight0[complete$Chick, "weight"] - 1))
head(complete, 3)
```

4.)

The chicks on diet 3 gained the most weight out of all the different diets, while chicks on diet 1 gained the least amount of weight.
```{r}
day21 <- complete %>%
  filter(Time == 21)
ggplot(data = day21, aes(x = Diet, y = weightGain)) + geom_boxplot()
```

5.)

The chick that gained the least amount of weight was chick 24 which was on diet 2 and only gianed 33gm. Chick 35 gined the most weight gaining a total of 331gm. Chick 35 was on the diet 3.
```{r}
ggplot(day21, aes(x = Chick, y = weightGain)) + geom_point()

day21 %>%
  arrange(weightGain) %>%
  head()

day21 %>%
  arrange(desc(weightGain)) %>%
  head()
```

6.)
```{r}
weight0.0 <- complete %>%
  filter(Time == 0)

weight0.0 %>%
  arrange(weight) %>%
  head()

weight0.0 %>%
  arrange(desc(weight)) %>%
  head()

follow <- complete %>%
  filter(Chick == 23 | Chick == 19 | Chick == 11 | Chick == 3 | Chick == 27 | Chick == 28 | Chick ==  29 | Chick == 33 | Chick == 36 | Chick == 48)

ggplot(follow, aes(x = Time, y = weight, colour=Chick)) + geom_point()
```

This graph shows the weight of each chick as a function of time. As you can see from the graph the starting weight of the chick does not have a significant impact on the overall weight of the chick at the end of the measurement period.

7.)

What I found intersting is how the diet of the chick affected the overall weight of the chicks.
```{r}
ggplot(follow, aes(x = Time, y = weight, colour=Diet)) + geom_point()
```
